Bayesian Sparsification of $\cplx$-valued networks

### 2019-11-04 paper/paper.tex
replace otimes with prod

Recall that we use fully factorized variational approximation for the parameters: $
  W \sim q(W)
    = \bigotimes_{ij} q(\omega_{ij})
$ with proper complex Gaussian distributions of each element $
  q(\omega_{ij})
    = \mathcal{N}^{\cplx}\bigl(
      \omega_{ij} \big\vert
      \mu_{ij}, \sigma^2_{ij}, 0
    \bigr)
$. Assuming factorized prior belief $\pi(W)$ on the parameters $W$, the KL-divergence
term in ELBO \eqref{eq:elbo} is
\begin{equation}  \label{eq:elbo-general-kl-div}
KL(q(W) \| \pi(W))
  % = \mathbb{E}_{W \sim q(W)} \log \tfrac{q(W)}{\pi(W)}
  % = \sum_{ij} \mathbb{E}_{\omega_{ij} \sim q(\omega_{ij})}
  %   \log \tfrac{q(\omega_{ij})}{\pi(\omega_{ij})}
  = \sum_{ij} KL\bigl(
    q(\omega_{ij}) \| \pi(\omega_{ij})
  \bigr)
  \,.
\end{equation}
%
We shall omit the subscripts for brevity in the derivations in the next section, which
we begin with a derivation of the entropy of a proper $\cplx$-Gaussian.

>>>>

Recall that we use fully factorized variational approximation for the parameters: $
  W \sim q(W)
    = \prod_{ij} q(\omega_{ij})
$ with proper complex Gaussian distributions of each element $
  q(\omega_{ij})
    = \mathcal{N}^{\cplx}\bigl(
      \omega_{ij} \big\vert
      \mu_{ij}, \sigma^2_{ij}, 0
    \bigr)
$. Assuming factorized prior belief $\pi(W)$ on the parameters $W$, the KL-divergence
term in ELBO \eqref{eq:elbo} is
\begin{equation}  \label{eq:elbo-general-kl-div}
KL(q(W) \| \pi(W))
  % = \mathbb{E}_{W \sim q(W)} \log \tfrac{q(W)}{\pi(W)}
  % = \sum_{ij} \mathbb{E}_{\omega_{ij} \sim q(\omega_{ij})}
  %   \log \tfrac{q(\omega_{ij})}{\pi(\omega_{ij})}
  = \sum_{ij} KL\bigl(
    q(\omega_{ij}) \| \pi(\omega_{ij})
  \bigr)
  \,.
\end{equation}
%
We shall omit the subscripts for brevity in the derivations in the next section, which
we begin with a derivation of the entropy of a proper $\cplx$-Gaussian.
